### 2023-03-16 paper.tex
Updates from Overleaf

\begin{minipage}{0.7\textwidth}
\small
\textit{Abstract} -- Single-cell bisulfite sequencing (scBS) allows for assessing DNA methylation at single-base pair and single-cell resolution.
Analyzing the big data sets thus obtained requires preprocessing to reduce data size, improve signal over noise, and provide interpretability.
Typically, this is simply done by dividing the genome into large tiles and averaging in these.
We show that this coarse-graining dilutes signal, and suggest improved approaches to determine more informative regions to quantify methylation in, and a better quantitation method than simple averaging.
We demonstrate how our approach enables better distinguishing of cell types and reduces demands on cell number.
We also implement an approach to detect differentially methylated regions (DMRs) between groups of cells.
Finally, we present a software tool, \texttt{scbs}, that implements these methods and offers further functionality required to work with scBS data.
\end{minipage}
\vspace{6.5ex}
}]

@@

The standard approach to analyze scBS-seq data is based on methodology developed for the analysis of scRNA-seq data.
Therefore, we start by briefly reviewing how sc\emph{RNA}-seq data is commonly analyzed, before we discuss scBS data analysis.

The starting point in most scRNA-seq analyses is a matrix of UMI counts (i.e.
of counts of distinct RNA molecules), one row for each cell and one column for each gene.
A first goal is usually to assign cell types or states to cells.
To this end, one needs to establish which cells are similar to each other, i.e., quantify the distance (i.e., dissimilarity) between any two given cells' transcriptional profile.
A standard approach, used with minor variation in virtually all recent research and automated by popular software such as Seurat \citep{Hao_2021} or ScanPy \citep{Wolf_2018}, is as follows: One first accounts for cell-to-cell variation in sequencing depth by dividing each UMI count by the respective cell's total UMI count, then transforms to a homoskedastic scale by taking the logarithm.
\textbf{In order to avoid matrix elements with zero count to be transformed to minus infinity, one typically adds a very small ``pseudocount'' (often $10^{-4}$) to the normalized fractions before taking the logarithm.}  % is this even correct?
Now, one could use Euclidean distances of these vectors of logarithmized fractions as dissimilarity score.
However, these scores would be exceedingly noisy due to the strong Poisson noise introduced by the many genes with very low counts.
Therefore, one performs a principal component analysis (PCA), keeping only the top few (typically, 20 to 50) components.
As Poisson noise is uncorrelated between genes, it will average out in the top principal components, as these are all linear combinations with weight on a large number of genes.
Therefore, Euclidean distances between these ``PCA space'' vectors provide a robust dissimilarity score.
Hence, the PCA space representation is suitable as input to methods like t-SNE and UMAP, which provide a two-dimensional representation of the data, or to methods for clustering (assigning cells to groups by similarity) and trajectory finding (identifying elongated manifolds in PCA space and assigning cells to quasi-1D positions along them).

@@

While this simple procedure is straight-forward and produces satisfactory results, the coarse resolution of large genomic tiles and the sparse read coverage of single-cell methylomes still pose significant challenges in the analysis of scBS data.
Here, we propose three improvements that, as we show afterwards, considerably increase the information content of the processed data.
We will first explain the proposed improvement in a qualitative manner, while mathematical details are given later in the Methods section.
Then, we will demonstrate the improvement using benchmarks.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=\columnwidth]{figures/Fig_sliding.png}
    \end{center}
    \caption{\small \textbf{Finding variably methylated regions.}\\
    The chromosomes are divided up into overlapping windows (first five shown at the bottom), and for each window, the cells' methylation values are calculated as described and as depicted in Fig.~\ref{fig:smoothres}B.
    Then, the variance of these values is calculated (each point represents one of the overlapping windows), a threshold (dashed line) is chosen such that a chosen quantile of windows have a variance exceeding the threshold.
    Windows with above-threshold variance are merged if they overlap, yielding the ``variably methylated regions'' (VMRs).}
    \label{fig:vmr}
\end{figure}

@@

\begin{figure*}
    \begin{center}
    \includegraphics[width=.65\textwidth]{figures/Fig_DMRdetection.png}
    \end{center}
    \caption{\small \textbf{Identification of differentially methylated regions.}\\
    The chromosome is divided into windows overlapping by a small and fixed size.
    For each window, the cell’s methylation values are calculated as described and as depicted in Fig.~\ref{fig:smoothres}B.
    Then the t-statistic of these values is obtained as a measure of methylation difference (each point represents one of the windows).
    Upper and lower thresholds (dashed lines) are chosen such that a defined quantile of windows have a t-statistic above or below the threshold.
    Windows exceeding either threshold are merged if they overlap, yielding the differentially methylated regions (DMRs).}
    \label{fig:dmrscan}
\end{figure*}

@@

\subsection{Utility of DMRs and VMRs} % not sure if we need a subsection here

While the primary purpose of VMRs is to provide better input for the distance calculations, their small size also means that they can be readily compared with genomic annotation, which aids in their functional interpretation.
Large 100~kb tiles will often contain multiple genes with distinct expression patterns, small VMRs located in known regulatory elements or gene bodies are more easily associated with individual genes and their associated function.
Thus, VMRs provide a useful starting point for examining the data with methods from functional genomics.
To enable a targeted characterization of epigenomic and gene regulatory differences between conditions or cell types, the same principles may also be applied to DMRs.

@@

\begin{figure*}
    \begin{center}
    \includegraphics[width=.65\textwidth]{figures/Fig_correlation.png}
    \end{center}
    \caption{\small \textbf{Correlation of DNA methylation and gene expression}.\\
    \textbf{(A)} Distribution of Pearson correlations between gene expression and promoter methylation (black) and gene expression and methylation of the nearest VMR (red).
    \textbf{(B)} Correlation of each gene's RNA expression values to methylation (shrunken mean of residuals) at promoters (y-axis), or to methylation of the nearest VMR (x-axis).
    Promoters are defined as intervals \textpm2~kb around the TSS.
    \textbf{(C)} Mean methylation near the gene Htra1 (ENSMUSG00000006205).
    Cells are assigned to 4 groups based on Htra1 expression (group 0: cells with no Htra1 expression, groups 1-3: cells that express Htra1, divided into three equally large groups with group 3 having the highest expression).
    Data from \citet{kremer_scnmt}.}
    \label{fig:correlation}
\end{figure*}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=0.7\textwidth]{figures/Fig_benchmark.png}
    \end{center}
    \caption{\small \textbf{Benchmark of our methods on single-cell multi-omic data of cells of the murine forebrain}.\\
    \textbf{(A)} Cell labels based on clustering of single-cell transcriptomes from \citet{kremer_scnmt}.
    \textbf{(B, C)} Exemplary UMAPs obtained when analyzing the data set with our proposed methods (B) or conventional methods based on genome tiling (C).
    \textbf{(D, E)} Mean neighbor score \textbf{(D)} obtained after analysing single-cell methylomes with different combinations of methods.
    Either 100~kb genomic tiles or VMRs were subjected to PCA and UMAP.
    Tiles or VMRs were pre-processed as proposed in this work (shrunken mean of residuals subjected to iterative PCA) or using conventional methods (PCA on lightly imputed methylation percentages, based on \citep{luo2017single}).
    The full 1566-cell data set was sub-sampled to simulate smaller data sets (x axis).
    A higher neighbor score implies better separation of cell types inferred from single-cell transcriptomes of the same cells \textbf{(A)}.
    }
    \label{fig:score}
\end{figure*}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=.8\textwidth]{figures/Fig_workflow.png}
    \end{center}
    \caption{\small \textbf{Overview of the functionalities implemented in the \texttt{scbs} package.}\\
        \texttt{scbs prepare} parses methylation files produced by common bisulfite sequencing mappers and stores their contents in a compressed format optimised for efficient access to genomic intervals.
        \texttt{scbs} also produces cell-wise summary statistics and quality plots (here: average methylation around the transcription start site) that are used to detect low-quality cells.
        These cells can be discarded with \texttt{scbs filter}.
        To obtain a methylation matrix, similar to the count matrices used in scRNA-seq, the user must first decide in which genomic intervals methylation should be quantified.
        The user may either provide genomic regions of \emph{a priori} interest, or they may choose to discover VMRs (variably methylated regions) in the data with \texttt{scbs scan}.
        The resulting methylation matrix can then be used for downstream analysis such as cell clustering and dimensionality reduction.
        Identified groups of cells (e.g. clusters) can then be scanned for DMRs with \texttt{scbs diff}.
    }
    \label{fig:workflow}
\end{figure*}

We have implemented the approach just described in a Python package with a command line interface, called \texttt{scbs}, which also offers a number of other functionalities for the analysis of scBS data (Figure \ref{fig:workflow}).
The starting point of such an analysis are methylation files generated by tools such as Bismark \citep{bismark}, methylpy \citep{methylpy} or biscuit \citep{biscuit}.
For each cell, these tools produce a text file that lists the methylation status of all CpG sites.
Since it is inconvenient to work with hundreds or thousands of text files, \texttt{scbs} provides the \texttt{prepare} command which parses these methylation files and stores their content in a compressed format that enables efficient access to all CpG sites of the genome.
\texttt{scbs prepare} is flexible and accepts all tabular input formats including Bismark .cov-files, methylpy .allc-files, or custom user-defined formats.

@@

\subsection{Re-analysis of published scBS datasets}
To re-analyze scBS data from \citet{kremer_scnmt}, single-cell CpG methylation reports were first stored with \texttt{scbs prepare} and then smoothed with \texttt{scbs smooth} using the default bandwidth of 1000~bp.
The mm10 mouse genome was then annotated with genomic intervals that were either obtained by tiling the genome into non-overlapping 100~kb tiles, or by acquiring VMRs with \texttt{scbs scan} using the current default options (bandwidth $=2000$, stepsize $=10$, variance threshold $= 0.02$, minimum cell requirement $=6$).
Methylation fractions, commonly represented as percentages, and the shrunken means of residuals were quantified with \texttt{scbs matrix} for both VMRs and tiles.
The same analysis was repeated for scBS data from \citet{luo2017single}, and for smaller data sets generated by randomly sub-sampling cells separately from both data sets.
For each data set, we thus obtained four methylation matrices:
either 100~kb tiles or VMRs, quantified either by simple averaging (methylation fractions) or with the shrunken mean of the residuals.
All four matrices were then subjected to PCA.
In the case of methylation fractions, we closely followed methods described in \citet{luo2017single}:
We selected tiles spanning $\ge20$ CpG sites and with sequencing coverage in at least 70\% of cells.
We then imputed missing values by imputing the mean for each tile, centered the values, and performed PCA.
In the case of VMRs, we used iterative PCA to handle missing values, as described earlier.
For visualization, the first 15 PCs were subjected to UMAP with parameters min\_dist $=0.2$, init $=$ "spca", and n\_neighbors $=\frac{\sqrt{n}}{1.5}$ where $n$ is the total cell number, to adapt to data sets of different size.

\subsection{Mean neighbor score} \label{methods:score}
To assess performance of our methods, we employed a score that quantifies how well cell types (or cell states) are separated in 15-dimensional PCA space.
For data from \citet{luo2017single}, we used cell type labels that the authors manually curated based on CH-methylation.
For the multi-omic data set, we repeated the single-cell transcriptomics analysis described in \citet{kremer_scnmt} with two adjustments:
We did not filter off-target cells such as endothelial cells, and we annotated cell types using Leiden clustering with the Seurat \citep{seurat} function \texttt{FindClusters(resolution = 0.1)}.
The score, based on the $\Gamma$-score \citep{Kireeva_2014}, varies between 0 and 1, where higher scores reflect better separation of cell types.
For each cell $j$, we count how many of its $k$ nearest neighbors have been assigned to the same cell type as cell $j$.
We denote this count $a^k_j$, where we have chosen $k=\frac{\sqrt{n}}{1.5}$.
The overall score used to evaluate a given combination of methods is then simply the mean of all cell-wise scores.

@@

\newpage
\section{Supplementary Figures}

@@

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.8\columnwidth]{figures/SFig_benchmark.png}
    \end{center}
    \caption{\small \textbf{Benchmark of our methods on single-cell methylomes of neural subtypes of the murine frontal cortex}.\\
    Our methods were benchmarked on single-cell methylomes from \citet{luo2017single} as described in Fig.~\ref{fig:score}.
    }
    \label{fig:score_luo}
\end{figure*}

\begin{figure*}
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/SFig_parameter_sweep.png}
    \end{center}
    \caption{\small \textbf{Effect of VMR detection parameters on separation of cell types}.\\
    \textbf{(A-B)} Mean neighbor scores obtained after analyzing single-cell methylomes from \citet{kremer_scnmt} (\textbf{A}) or \citet{luo2017single} (\textbf{B}) with our proposed methods.
    VMRs were detected with \texttt{scbs scan} using various sliding window bandwidths or variance thresholds, and on sub-samples of the full data sets.
    }
    \label{fig:sweep}
\end{figure*}

>>>>

\begin{minipage}{0.7\textwidth}
\small
\textit{Abstract} -- Single-cell bisulfite sequencing (scBS) allows for assessing DNA methylation at single-base pair and single-cell resolution.
Analyzing the big data sets thus obtained requires preprocessing to reduce data size, improve signal over noise, and provide interpretability.
Typically, this is simply done by dividing the genome into large tiles and averaging in these.
We show that this coarse-graining dilutes signal, and suggest improved approaches to determine more informative regions to quantify methylation in, and a better quantitation method than simple averaging.
We demonstrate how our approach enables better distinguishing of cell types and reduces demands on cell number.
We also implement an approach to detect differentially methylated regions (DMRs) in scBS data.
DMRs detected between oligodendrocytes and neural stem cells occur near genes related to myelination and stem cell maintenance respectively.
These represent core functions of these cell types, which highlights our ability to detect biologically meaningful DMRs.
Finally, we present a software tool, \texttt{scbs}, that implements these methods and offers further functionality required to work with scBS data.
\end{minipage}
\vspace{6.5ex}
}]

@@

The standard approach to analyze scBS-Seq data is based on methodology developed for the analysis of scRNA-seq data.
Therefore, we start by briefly reviewing how sc\emph{RNA}-seq data is commonly analyzed, before we discuss scBS data analysis.

The starting point in most scRNA-seq analyses is a matrix of UMI counts (i.e. of counts of distinct RNA molecules), one row for each cell and one column for each gene.
A first goal is usually to assign cell types or states to cells.
To this end, one needs to establish which cells are similar to each other, i.e., quantify the distance (i.e., dissimilarity) between any two given cells' transcriptional profile.
A standard approach, used with minor variation in virtually all recent research and automated by popular software such as Seurat \citep{Hao_2021} or ScanPy \citep{Wolf_2018}, is as follows: One first accounts for cell-to-cell variation in sequencing depth by dividing each UMI count by the respective cell's total UMI count, then transforms to a homoskedastic scale by taking the logarithm.
\textbf{In order to avoid matrix elements with zero count to be transformed to minus infinity, one typically adds a very small ``pseudocount'' (often $10^{-4}$) to the normalized fractions before taking the logarithm.}  % is this even correct? -L
Now, one could use Euclidean distances of these vectors of logarithmized fractions as dissimilarity score.
However, these scores would be exceedingly noisy due to the strong Poisson noise introduced by the many genes with very low counts.
Therefore, one performs a principal component analysis (PCA), keeping only the top few (typically, 20 to 50) components.
As Poisson noise is uncorrelated between genes, it will average out in the top principal components, as these are all linear combinations with weight on a large number of genes.
Therefore, Euclidean distances between these ``PCA space'' vectors provide a robust dissimilarity score.
Hence, the PCA space representation is suitable as input to methods like t-SNE and UMAP, which provide a two-dimensional representation of the data, or to methods for clustering (assigning cells to groups by similarity) and trajectory finding (identifying elongated manifolds in PCA space and assigning cells to quasi-1D positions along them).

@@

While this simple procedure is straight-forward and produces satisfactory results, the coarse resolution of large genomic tiles and the sparse read coverage of single-cell methylomes still pose significant challenges in the analysis of scBS data.
Here, we propose three improvements that, as we show afterwards, considerably increase the information content of the processed data.
We will first explain the proposed improvement in a qualitative manner, while mathematical details are given later in the Methods section.
Then, we will demonstrate the improvement using benchmarks.
Finally, we describe an approach to detect differentially methylated regions (DMRs) in scBS data, and showcase it on real data.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.85\columnwidth]{figures/Fig_sliding.png}
    \end{center}
    \caption{\small \textbf{Finding variably methylated regions.}\\
    The chromosomes are divided up into overlapping windows (first five shown at the bottom), and for each window, the cells' methylation values are calculated as described and as depicted in Fig.~\ref{fig:smoothres}B.
    Then, the variance of these values is calculated (each point represents one of the overlapping windows), a threshold (dashed line) is chosen such that a chosen quantile of windows have a variance exceeding the threshold.
    Windows with above-threshold variance are merged if they overlap, yielding the ``variably methylated regions'' (VMRs).}
    \label{fig:vmr}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/Fig_DMRdetection.png}
    \caption{\small \textbf{Identification of differentially methylated regions.}\\
    The chromosome is divided into windows overlapping by a small and fixed size.
    For each window, the cell’s methylation values are calculated as described and as depicted in Fig.~\ref{fig:smoothres}B.
    Then the t-statistic of these values is obtained as a measure of methylation difference (each point represents one of the windows).
    Upper and lower thresholds (dashed lines) are chosen such that a defined quantile of windows have a t-statistic above or below the threshold.
    Windows exceeding either threshold are merged if they overlap, yielding the differentially methylated regions (DMRs).}
    \label{fig:dmrscan}
\end{figure}

@@

While the primary purpose of VMRs is to provide better input for PCA and distance calculations, DMR detection facilitates the discovery of epigenetic differences between conditions or cell types.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=.95\columnwidth]{figures/Fig_correlation.png}
    \end{center}
    \caption{\small \textbf{Correlation of DNA methylation and gene expression}.\\
    \textbf{(A)} Distribution of Pearson correlations between gene expression and promoter methylation (black) and gene expression and methylation of the nearest VMR (red).
    \textbf{(B)} Correlation of each gene's RNA expression values to methylation (shrunken mean of residuals) at promoters (y-axis), or to methylation of the nearest VMR (x-axis).
    Promoters are defined as intervals \textpm2~kb around the TSS.
    \textbf{(C)} Mean methylation near the gene Htra1 (ENSMUSG00000006205).
    Cells are assigned to 4 groups based on Htra1 expression (group 0: cells with no Htra1 expression, groups 1-3: cells that express Htra1, divided into three equally large groups with group 3 having the highest expression).
    Data from \citet{kremer_scnmt}.}
    \label{fig:correlation}
\end{figure}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{figures/Fig_benchmark.png}
    \end{center}
    \caption{\small \textbf{Benchmark of our methods on single-cell multi-omic data of cells of the murine forebrain}.\\
    \textbf{(A)} Cell labels based on clustering of single-cell transcriptomes from \citet{kremer_scnmt}.
    \textbf{(B, C)} Exemplary UMAPs obtained when analyzing the data set with our proposed methods (B) or conventional methods based on genome tiling (C).
    \textbf{(D, E)} Mean neighbor score \textbf{(D)} obtained after analysing single-cell methylomes with different combinations of methods.
    Either 100~kb genomic tiles or VMRs were subjected to PCA and UMAP.
    Tiles or VMRs were pre-processed as proposed in this work (shrunken mean of residuals subjected to iterative PCA) or using conventional methods (PCA on lightly imputed methylation percentages, based on \citep{luo2017single}).
    The full 1566-cell data set was sub-sampled to simulate smaller data sets (x axis).
    A higher neighbor score implies better separation of cell types inferred from single-cell transcriptomes of the same cells \textbf{(A)}.
    }
    \label{fig:score}
\end{figure*}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=.8\textwidth]{figures/Fig_workflow.png}
    \end{center}
    \caption{\small \textbf{Overview of the functionalities implemented in the \texttt{scbs} package.}\\
        \texttt{scbs prepare} parses methylation files produced by common bisulfite sequencing mappers and stores their contents in a compressed format optimised for efficient access to genomic intervals.
        \texttt{scbs} also produces cell-wise summary statistics and quality plots (here: average methylation around the transcription start site) that are used to detect low-quality cells.
        These cells can be discarded with \texttt{scbs filter}.
        To obtain a methylation matrix, similar to the count matrices used in scRNA-seq, the user must first decide in which genomic intervals methylation should be quantified.
        The user may either provide genomic regions of \emph{a priori} interest, or they may choose to discover VMRs (variably methylated regions) in the data with \texttt{scbs scan}.
        The resulting methylation matrix can then be used for downstream analysis such as cell clustering and dimensionality reduction.
        Identified groups of cells (e.~g. clusters) can then be scanned for DMRs with \texttt{scbs diff}.
    }
    \label{fig:workflow}
\end{figure*}

We have implemented the approach just described in a Python package with a command line interface, called \texttt{scbs}, which also offers a number of other functionalities for the analysis of scBS data (Figure \ref{fig:workflow}).
The starting point of such an analysis are methylation files generated by tools such as Bismark \citep{bismark}, methylpy \citep{methylpy} or BISCUIT.
For each cell, these tools produce a text file that lists the methylation status of all CpG sites.
Since it is inconvenient to work with hundreds or thousands of text files, \texttt{scbs} provides the \texttt{prepare} command which parses these methylation files and stores their content in a compressed format that enables efficient access to all CpG sites of the genome.
\texttt{scbs prepare} is flexible and accepts all tabular input formats including Bismark .cov-files, methylpy .allc-files, or custom user-defined formats.

@@

\subsection{Re-analysis of published scBS datasets}
To re-analyze scBS data sets by \citet{kremer_scnmt} and \citet{luo2017single}, the genome was first annotated with genomic intervals that were either obtained by tiling the genome into non-overlapping 100~kb tiles, or by acquiring VMRs with \texttt{scbs scan} using the current default options (bandwidth $=2000$, stepsize $=10$, variance threshold $= 0.02$).
VMRs with sequencing coverage in less than 
% WIP
For all intervals (VMRs and 100~kb tiles), the mean methylation fractions and the shrunken means of the residuals were obtained with \texttt{scbs matrix}.

Regions observed in less than four measured CpGs, or that were measured in less than 10\% of cells, were discarded.
To select $n$ intervals for further analysis, the top $n$ intervals were picked based on the number of cells that the region was measured in.

For dimensionality reduction, missing values were imputed with the iterative PCA described in the previous section.
To visualize data, UMAP was performed on the final 15 principal components.

\subsection{Nearest neighbor count score} \label{methods:score}
To assess performance of our methods, we processed mouse CpG methylation data from \citet{luo2017single} with several method combinations and scored each result.
The score evaluates the ability of each method combination to separate cell types in 15-dimensional PCA space, based on their CpG methylation.
Each score varies between 0 and 1, where higher scores reflect better separation.

Our nearest-neighbor-count score $\text{nnc}_k$, is based on the $\Gamma$-score \citep{Kireeva_2014} and is calculated as follows.
For each cell $j$, we count how many of its $k$ nearest neighbors have been assigned to the same cluster as cell $j$.
We denote this count $a^k_j$.
We consider a cell as ``well-assigned'' if $a^k_j>\theta k$, where we have chosen $\theta=0.9$.
In other words, a cell is ``well-assigned'' if at least 90\% of its $k$ nearest neighbors have been assigned to the same class as the cell under consideration.

The score $\text{nnc}_k$ is then simply the fraction of cells in the data set that are well-assigned in this sense.

@@

\section{Supplementary Figures}

@@

\begin{figure*}[h]
    \begin{center}
        \includegraphics[width=0.8\columnwidth]{figures/SFig_benchmark.png}
    \end{center}
    \caption{\small \textbf{Benchmark of our methods on single-cell methylomes of neural subtypes of the murine frontal cortex}.\\
    Our methods were benchmarked on single-cell methylomes from \citet{luo2017single} as described in Fig.~\ref{fig:score}.
    }
    \label{fig:score_luo}
\end{figure*}

\begin{figure*}[h]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/SFig_parameter_sweep.png}
    \end{center}
    \caption{\small \textbf{Effect of VMR detection parameters on separation of cell types}.\\
    \textbf{(A-B)} Mean neighbor scores obtained after analyzing single-cell methylomes from \citet{kremer_scnmt} (\textbf{A}) or \citet{luo2017single} (\textbf{B}) with our proposed methods.
    VMRs were detected with \texttt{scbs scan} using various sliding window bandwidths or variance thresholds, and on sub-samples of the full data sets.
    }
    \label{fig:sweep}
\end{figure*}
